---
title: "Results"
author: "Glenn Williams"
date: "14<sup>th</sup> August, 2019 (Last updated: `r format(Sys.time(), '%d<sup>th</sup> %B, %Y')`)"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

packages <- c(
  "tidyverse",
  "rlang",
  "here",
  "brms",
  "tidybayes",
  "bayestestR",
  "modelr",
  "ggforce",
  "ggrepel",
  "ggridges",
  "irr",
  "papaja" # install with devtools::install_github("crsh/papaja")
)

# load packages
lapply(packages, library, character.only = TRUE)

# load functions
r_function_list <- list.files(
  path = here("R", "00_functions"), 
  pattern = "R$",
  full.names = TRUE
)
purrr::walk(r_function_list, source)

# get citations
citations <- purrr::map(packages, citation)

# get file paths ----

# get model summaries only for easy loading
fitted_models_dir <- list.files(
  path = here("04_analysis", "01_models"),
  pattern = "rds$",
  full.names = TRUE
) %>% 
  str_subset("summary")
  

model_summaries_dir <- list.files(
  path = here("04_analysis", "02_summaries", "02_full-data"),
  pattern = "csv$",
  full.names = TRUE
)

plots_dir <- list.files(
  path = here("03_plots", "02_full-data"),
  pattern = "png$",
  full.names = TRUE
)

# load data ----

fitted_models <- purrr::map(fitted_models_dir, read_rds)

names(fitted_models) <- fitted_models_dir %>% 
  sub(".*/", "", .) %>% 
  substr(., 1, nchar(.)-4)

model_summaries <- purrr::map(model_summaries_dir, read_csv)
names(model_summaries) <- model_summaries_dir %>% 
  sub(".*/", "", .) %>% 
  substr(., 1, nchar(.)-4)
```

```{r define-renaming-variables}
summary_oldnames <- c(".value", "interval")
summary_newnames <- c("median", "percentile interval")
summary_drop <- c(".point", ".interval")

posterior_oldnames <- c("Ci Interval", "Rope Interval", "Pd")
posterior_newnames <- c("Percentile Interval", "HDI Interval", "P(Direction)")
posterior_drop <- c(
  ".width",
  ".point",
  ".interval",
  "CI",
  "ROPE_low", 
  "ROPE_high",
  "ROPE_Equivalence"
)
```

```{r get-citations}
my_citations <- papaja::cite_r(
  file = here("05_reports", "r-references.bib"), 
  pkgs = packages, 
  withhold = FALSE
)
```

`r my_citations` were used for data preparation, analysis, and presentation.

# Testing Phase Model

## Simple Effect of Variety Exposure within Each Task



Effect of language variety within each task in Supplemental (pre-reg predictions):

-	Overall performance is better in the dialect vs. no dialect condition. (dialect benefit)
-	Overall performance is better in the social than dialect condition. (less cognitive load and confusion between varieties).
-	Overall performance is better in dialect literacy than social due to training in multiple varieties highlighting the alphabetic principle, pushing people to the best strategy earlier on in learning.

